### 2023-10-16 2.State/nn.tex
Bunch of changes, going back to nn, rebooting

Analog computation enables those same calculations almost instantly and being far more power-efficient. This can be done using the physical properties of electrical devices.
We want to reproduce one of those neural network using electrical circuits to perform the same computation that a computer would in much faster manner.
Using \hyperref[subsec:memristors]{memristors} as weights. This removes the need to copy the weights from the main memory

>>>>

\subsection{Training weights}

The weights values are obtained through training. This is done in a few steps :

\begin{enumerate}
  \item Generate random values for each weight.
  \item Run the \ac{NN} to get an output vector.\label{step:restart}
  \item Measure error rate using the chosen error algorithm.
  \item Use the
  \item go back to \cref{step:restart}
\end{enumerate}

### 2023-10-16 2.State/rnn.tex
Bunch of changes, going back to nn, rebooting

\acp{RNN} are, as the name suggests, a type of \ac{NN} using recurrent connections. They are a \ac{NN} with at least one cycle within the structure, where outputs of the previous run is used the next one.

>>>>

\acp{RNN} are, as the name suggests, a type of \ac{NN} using recurrent connections. They are a \ac{NN} with at least one cycle within the structure, where outputs of the previous run is used the next one. Those feedback connections are what differenciates it from feedforward \ac{NN}.

This type of \ac{NN} is used when dealing with an unknown amount of inputs. Especially useful when treating timeseries \cite{rnn}. Example of \acp{RNN} uses are speech recognition, automatic language translation \cite{gru} and shape recognition, especially for handwriting recognition.

They are trained the same way \ac{NN} are, using backpropagation to measure the error and try adjusting the weights.

\subsection{Vanishing gradient problem}

The Vanishing gradient problem is a problem that comes when dealing with time depedent data.

\subsection{Simple \ac{RNN}}
